---
title: "Code"
author: "Szymon Lisowski"
date: "7/11/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "/Users/mr.fox/Github/COVID_wg_powiatow/Raw_data/danehistorycznepowiaty/")
```

## Loading necessary packages

```{r}
library(plyr)
library(dplyr)
library(readr)
library(tidyverse)
library(purrr)
library(downloader)
```

## Downloading data from URL

``` {r}
# https://datascienceplus.com/how-to-import-multiple-csv-files-simultaneously-in-r-and-create-a-data-frame/
url <- "https://arcgis.com/sharing/rest/content/items/e16df1fa98c2452783ec10b0aea4b341/data"
download(url, dest="/Users/mr.fox/Github/COVID_wg_powiatow/Raw_data/danehistorycznepowiaty/dataset.zip", mode="wb") 
unzip("/Users/mr.fox/Github/COVID_wg_powiatow/Raw_data/danehistorycznepowiaty/dataset.zip", exdir = "./")
```

## Reading data with no date column

When looking at the data I found that over time the data was subject to format changes. Date column was removed in 2020-12-24. The fix came only on 2021-01-27. This meant that I needed to add it manually and to limit the data.

``` {r}
files_1 <- list.files(path = "/Users/mr.fox/Github/COVID_wg_powiatow/Raw_data/danehistorycznepowiaty", pattern = ".csv")[31:65]

df_no_date <- ldply(.data = files_1, .fun = function(i) {read.csv(i, header = TRUE, sep = ";", dec = ",", stringsAsFactors = FALSE, na.strings = c("", "NA")) })

date_column <- data_frame(stan_rekordu_na = rep(seq.Date(as.Date("2020-12-24")-1, as.Date("2021-01-27")-1, by = "day"), 381)) %>% arrange(stan_rekordu_na)

df_date_1 <- cbind(df_no_date, date_column)
```

## Reading data before format changes

Once I managed to make those few csv format the same with the rest I found a different issue. After the 6th of Febrary 2022 the format changed once again now adding more data and also changing some column names. in code chunk below I work  to get the data compliant with those changes.

```{r}
files_2 <- list.files(path = "/Users/mr.fox/Github/COVID_wg_powiatow/Raw_data/danehistorycznepowiaty",pattern = ".csv")[1:441][-(31:65)]

df_date_2 <- ldply(.data = files_2, .fun = function(i) {read.csv(i, header = TRUE, sep = ";", dec = ",", stringsAsFactors = FALSE, na.strings = c("", "NA")) }) %>% mutate(stan_rekordu_na = as.Date(stan_rekordu_na))

model <- read.csv("/Users/mr.fox/Github/COVID_wg_powiatow/Raw_data/model.csv") %>% select(-1)

df_1 <- rbind(df_date_1, df_date_2) %>%
  right_join(model, by =  "teryt") %>%
  select(-c(1:2)) %>%
  relocate(c(wojewodztwo.y, powiat_miasto.y)) %>%
  dplyr::rename(wojewodztwo = wojewodztwo.y, 
                powiat_miasto = powiat_miasto.y, 
                liczba_nowych_zakazen = liczba_przypadkow,
                liczba_nowych_zakazen_na_10_tys_mieszkancow = liczba_na_10_tys_mieszkancow) %>%
  dplyr::mutate(across(!c(liczba_ozdrowiencow, stan_rekordu_na), ~ ifelse(is.na(.x), 0, .x))) %>%
  dplyr::arrange(stan_rekordu_na)
```

## Reading most up-to-date data

```{r}
files_3 <- list.files(path = "/Users/mr.fox/Github/COVID_wg_powiatow/Raw_data/danehistorycznepowiaty", pattern = ".csv")[-c(1:442)]

df_date_3 <- ldply(.data = files_3, .fun = function(i) {read.csv(i, header = TRUE, sep = ";", dec = ",", stringsAsFactors = FALSE, na.strings = c("", "NA")) }) %>% mutate(stan_rekordu_na = as.Date(stan_rekordu_na))

df_cor_3 <- df_date_3 %>%
  right_join(model, by =  "teryt") %>%
  select(-c(1:2)) %>%
  relocate(c(wojewodztwo.y, powiat_miasto)) %>%
  dplyr::rename(wojewodztwo = wojewodztwo.y, ) %>%
  dplyr::mutate(across(!c(liczba_ozdrowiencow, stan_rekordu_na), ~ ifelse(is.na(.x), 0, .x)))

write_csv(x = df_cor_3, file = "/Users/mr.fox/Github/COVID_wg_powiatow/Processed_data/Zakażenia_wg_powiatów_od_2022-02-08.csv")
```

## Joining all data

Finally, the data is the same across all the tables (of course, there are some data missing before 2022-02-06 date which I cannot fill). Now I can join everything together.

```{r}
df <- df_cor_3 %>% 
  select(-c(4,5,7,8)) %>%
  rbind(df_1) %>% 
  arrange(wojewodztwo, powiat_miasto, stan_rekordu_na)

write.csv(x = df, file = "/Users/mr.fox/Github/COVID_wg_powiatow/Processed_data/Zakażenia_wg_powiatów.csv")
```